Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-26 docs/manuscript/manuscript.tex

\section{Contribution}
Lack of water accessibility is a major crisis for many vulnerable people around the world. We have determined to seek literature reviews from the past 15 years to have the most up to date information because information on water accessibility is a topic that is constantly changing throughout the world due to different international, government, and even local policies. The literature review intends to investigate different journal articles on water accessibility in a global scale. Therefore we can conduct a research to fill many major gaps  to analyze the water accessibility predictor variables which could increase and enhance water accessibility in global scale. We will always gain new insight and wisdom on information about water accessibility through the global scale as we investigate and determine literature reviews chronologically. 
\citet{jagalsDoesImprovedAccess2006} highlights in a case study in a rural area in South Africa discovered providing small communities. The rural area used untreated river water as their water source. The Researchers installed good quality water with a piped distribution system and increase accessibility by installing communal taps. However, this implementation did not fall within the parameters of safe water. This didn't increase household quantities, which remained around 18 L per person per day. Their research
gives a potential understanding even making the drinking water accessible might not improve the quality of the water
itself.

@@

\citet{simaWaterFlowsEnergy2013} highlights the relation of the topic where it discovered that over 76 percent of the city's water
is utilized by less than ten percent of household piped water.  The study is focused on Kisumu Kenya and Sima
interviewed 260 informal water business operators. This article revealed a new insight where the majority of the
population in Kisumu relied on purchased water from kiosks (1.5 million $m^{3}$ per day) and used hand-drawn water-carts
(0.75 million $m^{3}$ per day)\citep{simaWaterFlowsEnergy2013}. Also, we discovered that the water trucking industry utilized the
most energy consumption and was high cost: water delivery trucks have the highest per cubic meter energy demand (35
$MJ/m^{3}$)\citep{simaWaterFlowsEnergy2013}.

@@

\citet{bartramGlobalMonitoringWater2014} highlights background information about the Millennium Development Goals. How it has
established global targets for drinking water and sanitation access (Bartram et al. 2014). The article indirectly gives
much information about progress towards focused targets, directed by international monitoring, has reduced the global
disease burden and improved the quality of life \citep{bartramGlobalMonitoringWater2014}. It utilizes a variety of sources such as
JMP, DHS, MICS surveys to analyze the data of many different locations in the world, therefore, it is a broad scope of
study of the progress of accessible and drinking water and sanitation globally. Our research can study further what
modes of transportation of clean drinking water would affect the progress of improving drinking water and sanitation in
one's community.

\citet{ondaCountryClusteringApplied2014} proposed a country typology based on nine water and sanitation indicators. They applied hierarchical clustering to 156 countries, accounting for 6.75 billion people (93\%). This work improves on previous geography or income-based country clustering.

@@

\citet{cassiviAccessDrinkingWater2018} highlights about how there should be more information to the effect of including a 30-minute
collection time to monitor access to drinking water. The lack of access to on-premises water sources can cause the use
of greater distant alternative sources. Therefore causing the quantity of retrieved water to reduce as the water plateau
phenomenon.\citet{cassiviAccessDrinkingWater2018} hypothesizes that the households who must travel further are using unimproved
sources. For our research, we can discover what modes of transportation people are traveling to retrieve the water and
in what quantity depending on their means of transportation. Therefore, learning how to decrease the travel time of
people to retrieve the water because according to the article, it can be a great burden and does not increase the
quality of one's life to retrieve water daily and far away from their homes.

>>>>

\section{Contribution}
Lack of water accessibility is a major crisis for many vulnerable people around the world. We have determined to seek literature reviews from the past 15 years to have the most up to date information because information on water accessibility is a topic that is constantly changing throughout the world due to different international, government, and even local policies. The literature review intends to investigate different journal articles on water accessibility in a global scale. Therefore we can conduct a research to fill many major gaps  to analyze the water accessibility predictor variables which could increase and enhance water accessibility in global scale. We will always gain new insight and wisdom on information about water accessibility through the global scale as we investigate and determine literature reviews chronologically. 
\subsection{2006-2016}
Improving water accessibility have been a priority by many organizations around the world, realizing it is the basic human rights to have clean and accessible drinkable water in past 15 years. During 2006 to 2016, overall water accessibility has been improving by utilizing the indicators of the past \citep{fullerTrackingProgressGlobal2016}. However, some researchers raises concerns on lack of clarity with the global water accessibility monitoring \citep{ondaGlobalAccessSafe2012, jiaHighResolutionSpatialDistribution2016}. However, in an era of rapidly changing advanced technologies, international, and government policies, some of the older research might not be adequate for up to date information for  example of The eight Millennium Development Goals (MDGs) upgrading into The Sustainable Development Goals (SDGs). In light of the newest SDGs of providing clean and accessible drinking water for all by 2030, researchers have devoted their study to understand water accessibility in global and specific country levels.

%  Several empirical studies have focused on Facebook usage in adolescent girls (Tiggermann & Slater, 2013; Meier & Gray, 2014) and in young adult women (Smith, Hames, & Joiner, 2013; Fardouly et al., 2015; Cohen, Newton-John & Slater, 2017), while a systematic review by Holland and Timmerman (2016) confirmed a relationship between social networking and body image for both women and men. Across these studies, there is consistent evidence that body image issues are influenced not by social media usage in general, but by engagement with the visual and interactive aspects of these platforms.

\citet{jagalsDoesImprovedAccess2006} highlights in a case study in a rural area in South Africa discovered providing small communities. The rural area used untreated river water as their water source. The Researchers installed good quality water with a piped distribution system and increase accessibility by installing communal taps. However, this implementation did not fall within the parameters of safe water. This didn't increase household quantities, which remained around 18 L per person per day. Their research
gives a potential understanding even making the drinking water accessible might not improve the quality of the water
itself.

@@

\citet{simaWaterFlowsEnergy2013} highlights topic where it discovered that over 76 percent of the Kenya's city's water
is utilized by less than ten percent of household piped water.  The study is focused on Kisumu Kenya and Sima
interviewed 260 informal water business operators. This article revealed a new insight where the majority of the
population in Kisumu relied on purchased water from kiosks (1.5 million $m^{3}$ per day) and used hand-drawn water-carts
(0.75 million $m^{3}$ per day)\citep{simaWaterFlowsEnergy2013}. Also, we discovered that the water trucking industry utilized the
most energy consumption and was high cost: water delivery trucks have the highest per cubic meter energy demand (35
$MJ/m^{3}$)\citep{simaWaterFlowsEnergy2013}.

@@

\citet{bartramGlobalMonitoringWater2014} highlights background information about the Millennium Development Goals. How it has
established global targets for drinking water and sanitation access. The article directly gives
much information about progress towards focused targets, directed by international monitoring, has reduced the global
disease burden and improved the quality of life \citep{bartramGlobalMonitoringWater2014}. It utilizes a variety of sources such as
JMP, DHS, MICS surveys to analyze the data of many different locations in the world, therefore, it is a broad scope of
study of the progress of accessible and drinking water and sanitation globally. Our research can study further what
modes of transportation of clean drinking water would affect the progress of improving drinking water and sanitation in
one's community.

\citet{ondaCountryClusteringApplied2014} proposed a country typology based on nine water and sanitation indicators in a global scale. They applied hierarchical clustering to 156 countries, accounting for 6.75 billion people (93\%). This work improves on previous geography or income-based country clustering.

@@

\subsection{2017-Present}
\citet{cassiviAccessDrinkingWater2018} highlights about how there should be more information to the effect of including a 30-minute
collection time to monitor access to drinking water. The lack of access to on-premises water sources can cause the use
of greater distant alternative sources. Therefore causing the quantity of retrieved water to reduce as the water plateau
phenomenon.\citet{cassiviAccessDrinkingWater2018} hypothesizes that the households who must travel further are using unimproved
sources. For our research, we can discover what modes of transportation people are traveling to retrieve the water and
in what quantity depending on their means of transportation. Therefore, learning how to decrease the travel time of
people to retrieve the water because according to the article, it can be a great burden and does not increase the
quality of one's life to retrieve water daily and far away from their homes.
